%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Devops Engineer} % Job title
    {Arrive} % Organization
    {Chicago, IL} % Location
    {Jan. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Completed migration to AWS from legacy colo.}
        \item {Owned and extend the deploy script process for new services and existing services needing to scale.}
        \item {Introduced Terraform to organization allowing reusable/testable infrastructure components.}
        \item {Added the first test and more to our Chef code base.}
        \item {Implemented monitoring and alerting platform(Graylog) to empower application developers with metrics.}
        \item {Worked with application teams to improve service application and security by lending AWS cloud expertise.}
        \item {Hardened AWS footprint in order to attain higher level of PCI Compliance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Uptake} % Organization
    {Chicago, IL} % Location
    {Apr. 2016 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of the build and deploy team tasked with increasing developer velocity.}
        \item {Deployed internal services using Chef and Terraform.}
        \item {Owned application responsible for deployment of 80+ microservices.}
        \item {Extended Jenkins with Groovy scripts allowing new services to onboard quickly}
        \item {Leveraged alerting stack to implement a dynamically scaling Jenkins agent build fleet.}
        \item {Worked with application teams to share Docker build and test knowledge.}
        \item {Created and tested disaster recovery plans for SCM and artifact store.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
